\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{color,xspace}
\usepackage{amssymb,amsmath,amsfonts,amsthm}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{boxedminipage}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage[sort]{natbib}
\usepackage{hyperref}
\renewcommand{\paragraph}[1]{\medskip\noindent{\bf #1}}

%\newcommand{\elaine}[1]{{\color{red}{[Elaine: #1]}}}
%\newcommand{\daniel}[1]{{\footnotesize[Daniel: #1]}}
%\newcommand{\aish}[1]{{\footnotesize[Aishwarya: #1]}}
%\newcommand{\jnote}[1]{{\color{blue}{[Jon: #1]}}}
\newcommand{\elaine}[1]{}
\newcommand{\jnote}[1]{}

\input{macros}

\begin{document}

\title{{\bf Non-Interactive Verifiable RAM Computation}}
%\author{{\small Anonymous Submission}}
\date{\vspace{-6mm}}
%\author{
%Daniel Apon\thanks{University of Maryland. Email: \{dapon,jkatz,elaine,aish\}@cs.umd.edu}
%\and Jonathan Katz$^*$
%\and Charalampos Papamanthou\thanks{University of California, Berkeley. Email: cpap@cs.berkeley.edu}
%\and Elaine Shi$^*$
%\and Aishwarya Thiruvengadam$^*$
%}

\maketitle

\begin{abstract}
Consider a client who wishes to outsource a large database to an
untrusted server, and subsequently would like to make queries
and updates to the database. The client wishes to guarantee
both privacy and verifiability.
Most existing %non-interactive \babis{interactive too}
verifiable computation
fail to address this problem satisfactorily, due to the fact
that the server's computation per query
is linear in the size of the database.

We propose non-interactive verifiable RAM computation -- since most
real-world database queries (e.g., range queries, binary search,
graph queries) can be implemented efficiently in the RAM model.
We propose two constructions: one that guarantees verifiability but
does not offer privacy; and a second one that guarantees both.
Our constructions have near-optimal efficiency: the server's computation
per query is not significantly more than the run-time of the
RAM program; the client's online computation per query is independent
of the run-time of the RAM, or the database size.

We show that our VC-RAM model is powerful, and give several applications.
Particularly, we show how to rely on verifiable-only VC-RAM
construction to build
\name schemes (i.e., oblivious
RAM with active server computation)
that consume asymptotically less bandwidth overhead
than existing oblivious RAM schemes, while ensuring
verifiability against an arbitrarily malicious server.
\end{abstract}

\noindent {\small {\bf Keywords}: verifiable RAM computation; verifiable oblivious storage;
oblivious RAM
}

\input{intro}
\input{prelim}
\input{vcram}
\input{vos}

%\section*{Acknowledgments}
%We thank  Bobby Bhattacharjee, Zvika Brakerski, Dov Gordon,
%   Raluca Ada Popa, Emil Stefanov, and Vinod Vaikuntanathan for useful discussions. 
%We also thank
%Sergey Gorbunov, Vinod Vaikuntanathan, and Hoeteck Wee
%for sharing an early manuscript of~\cite{GVW13} with us.

\bibliographystyle{abbrv}
\bibliography{refs,vc1,vc2,crypto,crypto2}


%\appendix
%\input{appendix}

\end{document}
